SunPy - Python for Solar Physics

### 2014-01-23 2-1-Map.tex

\subsection{Map}
Map is a 2D spatial data type, primarily used for images of the Sun and 
inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
\texttt{ndarray}) and gives easy access to standard meta data in the header of 
the image, via the \texttt{.meta} attribute as well as some convienience 
properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
\texttt{.wavelength} or \texttt{.coordinate\_system}.
The \texttt{Map} data type provides convenience methods for many functions 
such as, rotation and re-sampling as well as convenience visualisation 
functions, providing a easy to use as well as powerful interface.

@@

As can been seen in Listing \ref{code:aia_1} the map datatype parses header 
information for many purposes including visualisation on correct physical axes 
and limb plotting as well as making this information easily available to the 
user.

>>>>

\subsection{Map}
Map is a 2D spatial data type, primarily used for images of the Sun and 
inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
\texttt{ndarray}) and gives easy access to standard meta data in the header of 
the image, via the \texttt{.meta} attribute as well as some convienience 
properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
\texttt{.wavelength} or \texttt{.coordinate\_system}. Demonstrated in Listing 
\ref{code:aia_1} is this meta data parsing and `pretty printing' of the Map.
The \texttt{Map} object provides convenience methods for many functions 
such as, rotation and re-sampling as well as convenience visualisation 
functions, providing a easy to use as well as powerful interface.
Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.

@@

\texttt{GenericMap} is a subclass of \texttt{astropy.nddata.NDData} which is a 
generic wrapper around a \texttt{ndarray} with a \texttt{.meta} attribute, like 
\texttt{Map}. Having this inheritance structure with \texttt{astropy} provides 
potential for simple integration with other parts of \texttt{astropy} and other 
packages based on \texttt{astropy}, as \texttt{GenericMap} should form a 
drop-in replacement for \texttt{NDData}.

### 2014-01-23 2-Data_Types.tex

\subsection{Visualisation}
As has been demonstrated in this section, the core SunPy datatypes include 
visualisation code that is specialised to that data type. These visualisation 
methods all currently utilise the matplotlib package, and are designed in such 
a way that they integrate well with the pyplot functional interface of 
matplotlib, as demonstrated in Listing \ref{code:mpl_1}.

>>>>

\subsection{Visualisation}
\label{subsec:Viz}
As has been demonstrated in this section, the core SunPy datatypes include 
visualisation code that is specialised to that data type. These visualisation 
methods all currently utilise the matplotlib package, and are designed in such 
a way that they integrate well with the pyplot functional interface of 
matplotlib, as demonstrated in Listing \ref{code:mpl_1}.

### 2014-01-23 3-4-Helioviewer.tex
add pdf conversions of eps figures

SunPy provides the ability to download images from Helioviewer Project
servers.  The aim of the Helioviewer Project is to enable the
exploration of solar and heliospheric data from multiple data sources
(such as instrumentation and feature/event catalogs) via easy-to-use
visual interfaces.  The primary data provided by the Helioviewer
Project are images in the JPEG2000 format (for further details on the
Helioviewer Project see \cite{muller2009}\footnote{SunPy is used in Helioviewer 
production servers to manage the download and ingestion of JPEG2000
files from remote servers.}.)  The JPEG2000 files are typically
highly compressed compared to the source FITS files they are generated
from, and so can be a used as a shortcut to visualize large amounts of
data from multiple sources.

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0,
 width=512, height=512)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
available at \url{www.helioviewer.org}.}
\label{code:hv:downloadlatestpng}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 6, 
"[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50], \
[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example.eps}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
 instrument='HMI', detector='HMI', measurement='continuum')
from sunpy.map import Map
hmi = Map(filepath)
hmi.submap([200,550],[-400,-200]).peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map.eps}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy map object.}
\label{code:downloadjp2}
\end{listing}

>>>>

SunPy provides the ability to download images from Helioviewer Project 
servers.  The aim of the Helioviewer Project is to enable the exploration of 
solar and heliospheric data from multiple data sources (such as instrumentation 
and feature/event catalogs) via easy-to-use visual interfaces.  The primary 
data provided by the Helioviewer Project are images in the JPEG2000 format (for 
further details on the Helioviewer Project see \cite{muller2009} 
\footnote{SunPy is used in Helioviewer production servers to manage the 
download and ingestion of JPEG2000 files from remote servers.}.)  The JPEG2000 
files are typically highly compressed compared to the source FITS files they 
are generated from, and so can be a used as a shortcut to visualize large 
amounts of data from multiple sources.

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0,
 width=512, height=512)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
available at \url{www.helioviewer.org}.}
\label{code:hv:downloadlatestpng}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 6, 
"[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50], \
[SOHO,LASCO,C2,white-light,1,100]", x0=0, y0=0, width=768, height=768)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
filepath = hv.download_jp2('2012/07/05 00:30:00', observatory='SDO',
 instrument='HMI', detector='HMI', measurement='continuum')
from sunpy.map import Map
hmi = Map(filepath)
hmi.submap([200,550],[-400,-200]).peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy map object.}
\label{code:downloadjp2}
\end{listing}
